### 2014-03-14 src/methodology.Rnw
fix

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

>>>>

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
clean <- function(x) {
  sub('CONSTRUCTOR_CALLS','CC',
      sub('INCREMENTS','I',
        sub('RETURN_VALS','RV',
          sub('VOID_METHOD_CALLS','VMC',
            sub('NON_VOID_METHOD_CALLS','NMC',
              sub('RMSWITCH','RS',
                sub('REMOVE_CONDITIONALS','RC',
                  sub('REMOVE_INCREMENTS','RI',
                    sub('NEGATE_CONDITIONALS','NC',
                      sub('MATH','M',
                        sub('INVERT_NEGS','IN',
                          sub('INLINE_CONSTS','IC',
                            sub('EXPERIMENTAL_SWITCH','ES',
                              sub('EXPERIMENTAL_MEMBER_VARIABLE','EMV',
                                sub('DELETE_CONDITIONALS','DC',
                                  sub('CONDITIONALS_BOUNDARY','CB',x))))))))))))))))
}
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
